---
title: "Lab 00 - Hello IDS!"
author: "Paul Prentice"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Ayush", "Addison", "Chris", 
           "Paul W", "Adi"),
  github_username = c("ayushpgowda", "LeonTheGreat21", "ChisWang103", 
                      "paulhanwang", "adigos12"), 
  colour = c("purple", "green", "black", 
             "red", "grey"),
  hobby = c("cricket", "gaming", "gaming", 
            "sailing", "basketball"),
  favourite_number = c(10, 9, 8, 15, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


it shows their github usersname with a bar graph with the representing their favourite number and the bar being their favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub username", 
          y = "Favourite number",
          title = "WK1 group information graph")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A scattergraph with labels such as sport - non sport and team - single player
